\huge Tor's Usability for Censorship Circumvention

### 2016-04-12 pets2017-paper/pets2017-paper.tex
Add all-participant-edges.pdf to the paper.
Temporarily disable topology.png; it's not yet checked in.
Spelling of Isabela.

\begin{figure}
\centering
 \includegraphics[width=0.5\textwidth]{topology.png}
\caption{
The chain of components involved in connecting to a website over Tor.
Most users do not need a proxy;
similarly only those users who face a censor need a bridge.
In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
We have shown the bridge as separate component
because of the special role it plays.
When a bridge is used, it takes the place of the first Tor hop.
}
\label{fig:topology}
\end{figure}

@@

@@

\section {Acknowledgments}
{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabella Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.} 
{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}

>>>>

\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth]{topology.png}
\caption{
The chain of components involved in connecting to a website over Tor.
Most users do not need a proxy;
similarly only those users who face a censor need a bridge.
In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
We have shown the bridge as separate component
because of the special role it plays.
When a bridge is used, it takes the place of the first Tor hop.
}
\label{fig:topology}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics{all-participant-edges}
\caption{
Summary of participants' actions throughout the entire experiment.
Different colors indicate which screen was shown at each moment.
The overall length of the lines show the total time to completion,
except for those we cut off after approximately 40 minutes.
}
\label{fig:all-participant-edges}
\end{figure*}

@@

\section {Acknowledgments}
{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabela Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.} 
{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}
